---
title: "Class Example Task 1"
author: "Ben Woodruff"
date: "5/4/2021"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background

In here we'll put some background information. Grabbing it from online works.  

## Task 1
This code creates a data frame called “dist”. The dist data frame contains measurements for 202 light bulbs 2104 hours after the the light bulb was turned on.

```{r}
library(data4led)
dist <- led_time(2100)
```

The data frame named “dist” includes the columns (1) “id”, the identification number for your randomly selected bulb, (2) “hours”, the number of hours since the bulb has turned on, (3) “intensity”, the lumen output of the bulb, and (4) “percent_intensity”, the bulb intensity as a percent of the original lumen.

The histogram below shows the distribution of the "percent intensity" column. 

```{r}
hist(dist$percent_intensity,xlab='Percent Intensity',ylab='Count',main='Histogram of Percent Intensity', probability=TRUE)
```

From the histogram above, we can see that the percent intensities of the bulbs appear to follow some bell shaped distribution.  The center of this bell is around 101.5%.  

## Task 2

We will be exploring the following models. 

1. $f_0(L; a,b) = \frac{1}{b-a}$ with $-\infty < a < L < b < \infty$ (and 0 otherwise)
2. $f_1(L; h,a) = \frac{1}{\sqrt{2\pi a}}e^{-\frac{(x-h)^2}{2a}}$ with $h>0$, $a>0$, and $−\infty<L<\infty$
3. $f_2(L; h,a,b) = \frac{b^a}{\Gamma(a)}(L-h)^{a-1}e^{-b(L-h)}$ with $a>0$, $b>0$, and $L\geq h$ (and 0 otherwise)

### Model $f_0$
Let's examine the first model, $f_0$. 
The variable $a$ controls the starting point of the domain of the function, and similarly $b$ is the end point.  The function is constant.  Let's plot a couple representatives below. 

```{r}
f0 <- function(L,a=0,b=1){
  # Make sure a < b when using this function.
  
  out <- rep(-1,length(L))
  out[(L <= a)] <- 0
  out[(a < L) & (L < b)] <- 1/(b-a) + 0*L[(a < L) & (L < b)]
  out[(L >=b)] <-0
  
  return(out)
}

b <- 102
a1 <- 97
L1 <- seq(a1,b,0.1)
y1 <- f0(L1,a1,b)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(L1,y1,type='l',xlim=c(90,110), ylim=c(0,0.35))

a2 <- 99
L2 <- seq(a2,b,0.1)
y2 <- f0(L2,a2,b)

plot(L2,y2,type='l',xlim=c(90,110), ylim=c(0,0.35))
mtext('Changing a in f0', side = 3, line = 0)

```

In the two plots above we chose $b=102$, and changed $a$ from 97 to 99.  Making $a$ closer to $b$ causes the graph to be narrow and higher.   We can similarly see what happens as we change $b$, which we will do in the plots below. 

```{r}
b1 <- 102
a <- 97
L1 <- seq(a,b1,0.1)
y1 <- f0(L1,a,b1)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(L1,y1,type='l',xlim=c(90,110), ylim=c(0,0.25))

b2 <- 109
L2 <- seq(a,b2,0.1)
y2 <- f0(L2,a,b2)

plot(L2,y2,type='l',xlim=c(90,110), ylim=c(0,0.25))
mtext('Changing a in f0', side = 3, line = 0)

```
In the plot above we fixed $a=97$ and then changed $b$ from 102 to 109.  Increasing $b$ caused the graph to be wider and shorter. 


### Model $f_1$
We now examine the second model, $f_1(L; h,a) = \frac{1}{\sqrt{2\pi a}}e^{-\frac{(x-h)^2}{2a}}$ with $h>0$, $a>0$, and $−\infty<L<\infty$. 
This model produces a mound shaped curve. The output of the function is all positive. The values increase until $h$, and then decrease after $h$. The variable $a$ controls how sharply the mound spikes upwards before dropping.  Let's view this in several examples. 

In the pictures below, we'll fix $a=2$ and then change $h$ from 99 to 102. Notice that the value of $h$ just causes the model to recenter the graph around the values $h$. 

```{r}
f1 <- function(L,h=0,a=1){
#Make sure h > 0 and a > 0.

1/sqrt(2*pi*a)*exp(-(L-h)^2/(2*a))
}

a <- 2
L <- seq(80,120,0.1)
h1 <- 99
y1 <- f1(L,h1,a)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(L,y1,type='l',xlim=c(80,120))

h2 <- 102
y2 <- f1(L,h2,a)

plot(L,y2,type='l',xlim=c(80,120))
mtext('Changing h in f1', side = 3, line = 0)
```

Now we'll fix $h=101$, and change the value of $a$ from 2 to 1, in the graph below, and focus on the fact that a smaller value for $a$ causes the graph to spike more rapidly (reaches a higher value over a smaller width). 

```{r}
a1 <- 2
L <- seq(80,120,0.1)
h <- 101
y1 <- f1(L,h,a1)

par(mfrow=c(1,2),mar=c(2.5,2.5,1,0.25))
plot(L,y1,type='l',xlim=c(80,120), ylim=c(0,0.5))

a2 <- 1
y2 <- f1(L,h,a2)

plot(L,y2,type='l',xlim=c(80,120), ylim=c(0,0.5))
mtext('Changing a in f1', side = 3, line = 0)

```

In summary, the parameter $h$ tells us where the peak of the mound is at, while the variable $a$ controld how tall peak gets to (as well as how wide the mound is). 


